Carbonate chemistry at Ny-Ålesund

### 2023-05-31 awipev-CO2.Rmd
Added chunk to calculate the time spent by REMOS at each depth group.

>>>>

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# we calculate the duration of each stop 
depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
tmp <- d_all %>% 
  dplyr::select(datetime, depth_group) %>%
  dplyr::filter(depth_group != "NA") %>% 
  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
```
